Optimizing the Robotics Closet

### 2018-11-30 paper.tex
removed todo
added link to code
made lines in tex file a decent size
added simplifying assumption

\textbf{\color{red} TODO: More related work}

\section{Assumptions}
Most items in the robotics closet are in boxes. As a result, we assume that all
items are rectangular prisms. Although items such as the chemicals or soldering irons
are not strictly rectangle-shaped, it would be strange for another item reached into
the empty areas of the items' bounding boxes. Taking advantage of this, we approximate
all items as being rectangular prisms, and measure their bounding boxes.
\par
We also assumed that certain parts of the robotics closet are not to be moved. For example, the shelf containing aluminum brackets and blocks for machining was excluded from the model entirely. This is due to the cumbersome nature of moving hundreds of unboxed chunks of metal, and due to opposition to its transportation by team members who frequently use it. The food pantry portion as well as some non-food items that made their way into it was similarly excluded after brief deliberation. Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since the access to other closets is unaffected by the contents of these.
\par
Another simplifying assumption we made is that all drawers have one unit of depth. In other words, we cannot insert items one behind another. This is a valid assumption to make because having to pull an item from behind another would drastically reduce the retrieval time of both items, undoing much of the benefits of our optimization. This can be adjusted to be a soft constraint (penalize heavily for items that are one behind another) if the model is infeasible without this change. In the meantime, we are reasonably confident that disallowing multiple units of depth is the best approach keeping in mind our ultimate goal of convenience.

\section{Model}
We collected data from the robotics closet by measuring each item and shelf. Each
shelf $s$ is represented as an ordered triple $(d, a, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $a$ is the area of the shelf, and
$c$ is the connected components to which the self belongs.
\par
Each item is represented with an ordered triple $(a, p, s)$, where $a$ is the area
of the item, $p$ is the probability that the item is selected, and $s$ is the item's
subsystem. Notice that we represent each item as a 2-dimensional area. This is valid
because we assumed that each shelf had a single unit of depth. As a preprocessing step,
we choose to minimize the area. However, we cannot rotate always the item into a
horizontal orientation. Therefore, $h$ is constant. For an item $i$ with length $l_i$,
width $w_i$, and height $h_i$, its area $a_i$ is given by 
$$a_i = \min(l_i, w_i) \cdot h_i$$
\par
Let there be $n$ shelves and $m$ items, $k$ subsystems, and $l$ is the number of
connected components. Our decision variables lie in two matrices
$$W = (w_{ij}), 1 \leq i \leq n, 1 \leq j \leq m$$
$$C = (c_{ij}), 1 \leq i \leq l, 1 \leq j \leq k$$
Each $w_{ij}$ and $c_{ij}$ is a binary variable, i.e. each $w_{ij}, c_{ij} \in {0, 1}$.
Each $w_{ij}$ is $0$ if item $j$ is not on shelf $i$ and $1$ otherwise. $c_{ij}$ is
$1$ if subsystem $j$ lies in connected component $i$ and $0$ otherwise. 
$C$ is a $l \times k$ matrix because there are l connected components and k subsystems. \\
Note about notation: $a^i_k$ indicates the area of item $k$ while $a^s_k$ indicates the
area of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 
\par
The model is subject to the following constraints:
\begin{enumerate}
\item $\sum_{j = 1}^{m}w_{ij}a^i_j \leq w^s_i, 1 \leq i \leq n$.
\item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
\item $\sum_{j = 1}^{l}c_{ji} = 1, 1 \leq i \leq k$.
\item Let $K$ be the set of indices of items belonging to subsystem $i$. Let
  Let $L$ be the set of indices of shelves belonging to connected component $j$.
  Then $\sum_{a \in K}\sum_{b \in L}w_{ba} = |K| \cdot c_{ji}, 1 \leq i \leq k, 1 \leq j \leq l$.
\end{enumerate}
Since each probability $p$ is less than 1, we incentivize putting items with higher probability
in the front by multiplying the probability by the distance. Thus, our objective function
becomes
$$\min z = \sum_{i = 1}^{n}\sum_{j = 1}^{m} d_j p_i w_{ij}$$

@@

\section{References}
\begin{thebibliography}{9}
\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
  Linear Programming.” Analytics Vidhya, 2016
\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
  Informatica e Sistemistica, University of Bologna, 2001
\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
\end{thebibliography}
\end{document}

>>>>

%\textbf{\color{red} TODO: More related work}

\section{Simplifying Assumptions}
Most items in the robotics closet are in boxes. As a result, we assume that all
items are rectangular prisms. Although items such as the chemicals or soldering irons
are not strictly rectangle-shaped, it would be strange for another item reached into
the empty areas of the items' bounding boxes. Taking advantage of this, we approximate
all items as being rectangular prisms, and measure their bounding boxes.
\par
We also assumed that certain parts of the robotics closet are not to be moved. For
example, the shelf containing aluminum brackets and blocks for machining was excluded
from the model entirely. This is due to the cumbersome nature of moving hundreds of
unboxed chunks of metal, and due to opposition to its transportation by team members
who frequently use it. The food pantry portion as well as some non-food items that
made their way into it was similarly excluded after brief deliberation. Excluding
parts of the closet from the model does not reduce the validity of the remaining
optimization since the access to other closets is unaffected by the contents of these.
\par
Another simplifying assumption we made is that all shelves have one unit of depth.
In other words, we cannot insert items one behind another. This is a valid assumption
to make because having to pull an item from behind another would drastically reduce the
retrieval time of both items, undoing much of the benefits of our optimization. This
can be adjusted to be a soft constraint (penalize heavily for items that are one
behind another) if the model is infeasible without this change. In the meantime, we
are reasonably confident that disallowing multiple units of depth is the best
approach keeping in mind our ultimate goal of convenience.
\par
Lastly, we assumed that there can be on average 3 items in the same 1-D linear
segment. We arrived at this assumption by noticing that the fast majority of
items are in the same type of box, which are 21 cm wide. Since shelf widths
range from 74 cm to 91 cm, 3 boxes fit comfortably on three shelves. This
also has the advantage of providing padding to the items to ease retrieval. 
\section{Model}
We collected data from the robotics closet by measuring each item and shelf. Each
shelf $s$ is represented as an ordered triple $(d, a, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $a$ is the area of the shelf, and
$c$ is the connected components to which the self belongs.
\par
Each item is represented with an ordered triple $(a, p, s)$, where $a$ is the area
of the item, $p$ is the probability that the item is selected, and $s$ is the item's
subsystem. Notice that we represent each item as a 2-dimensional area. This is valid
because we assumed that each shelf had a single unit of depth. As a preprocessing step,
we choose to minimize the area. However, we cannot rotate always the item into a
horizontal orientation. Therefore, $h$ is constant. For an item $i$ with length $l_i$,
width $w_i$, and height $h_i$, its area $a_i$ is given by 
$$a_i = \min(l_i, w_i) \cdot h_i$$
\par
Let there be $n$ shelves and $m$ items, $k$ subsystems, and $l$ is the number of
connected components. Our decision variables lie in two matrices
$$W = (w_{ij}), 1 \leq i \leq n, 1 \leq j \leq m$$
$$C = (c_{ij}), 1 \leq i \leq l, 1 \leq j \leq k$$
Each $w_{ij}$ and $c_{ij}$ is a binary variable, i.e. each $w_{ij}, c_{ij} \in {0, 1}$.
Each $w_{ij}$ is $0$ if item $j$ is not on shelf $i$ and $1$ otherwise. $c_{ij}$ is
$1$ if subsystem $j$ lies in connected component $i$ and $0$ otherwise. 
$C$ is a $l \times k$ matrix because there are l connected components and k subsystems. \\
Note about notation: $a^i_k$ indicates the area of item $k$ while $a^s_k$ indicates the
area of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 
\par
The model is subject to the following constraints:
\begin{enumerate}
\item $\sum_{j = 1}^{m}w_{ij}a^i_j \leq w^s_i, 1 \leq i \leq n$.
\item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
\item $\sum_{j = 1}^{l}c_{ji} = 1, 1 \leq i \leq k$.
\item Let $K$ be the set of indices of items belonging to subsystem $i$. Let
  Let $L$ be the set of indices of shelves belonging to connected component $j$.
  Then $\sum_{a \in K}\sum_{b \in L}w_{ba} = |K| \cdot c_{ji}, 1 \leq i \leq k, 1 \leq j \leq l$.
\end{enumerate}
Since each probability $p$ is less than 1, we incentivize putting items with higher probability
in the front by multiplying the probability by the distance. Thus, our objective function
becomes
$$\min z = \sum_{i = 1}^{n}\sum_{j = 1}^{m} d_j p_i w_{ij}$$

@@

\section{References}
\begin{thebibliography}{9}
\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
  Linear Programming.” Analytics Vidhya, 2016
\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
  Informatica e Sistemistica, University of Bologna, 2001
\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
\end{thebibliography}
Source code can be found at: https://github.com/save-buffer/math381
\end{document}
